Robot programming for dummies

### 2013-06-18 paper.tex
Added rviz section

\documentclass{article}
\begin{document}

@@

TBD: talk about simplicity vs expressiveness tradeoff here?

@@

\section{ROS}

Let's look at the state of the art in robot programming technology.

ROS provides a distributed publish/subscribe messaging platform for a collection of {\em nodes} to communicate with each other.

Before ROS, roboticists had to create the software to control their robots from scratch, each doing the same work to create device drivers and rebuild libraries for their specific robot's hardware.

ROS runs on 50-100 robots

>>>>

\documentclass{article}
\usepackage{graphicx}

\begin{document}

@@

\section{The state of the art}

ROS provides a distributed publish/subscribe messaging platform for a collection of {\em nodes} to communicate with each other. Each node encapsulates a small amount of robot functionality, and interfaces with the rest of the ROS ecosystem to make that functionality available through a common interface. For example, ROS nodes exist to stream video from webcams, control the motors in robot arms, plan a path from one point to another, and recognize graspable objects in an image.

Before ROS, roboticists had to create the software to control their robots from scratch, each doing the same work to create device drivers and rebuild libraries for their specific robot's hardware.  Now, ROS has been ported to around 100 different models of robots worldwide\footnote{http://www.ros.org/wiki/Robots}, enabling roboticists to quickly bring a new robot model online.

\begin{figure}[tbh]
\scalebox{0.15}{\includegraphics{rviz.png}}
\caption{RViz interface for controlling robots}
\label{rviz}
\end{figure}

However, ROS provides a fairly low-level interface to robot control. Designed for roboticists, the RViz interface (Figure~\ref{rviz}) displays all the sensor feeds coming from the robot and lets one send low-level motion commands to the robot such as rolling forward or rotating the shoulder joint. In the figure, a robot is shown examining objects on a table in front of it. The green pattern represents the data from a depth sensor mounted on the robot's head, whereas the purple line represents the walls detected by a laser rangefinder mounted on the robot's base. The tricolored axes display the various coordinate frames in use, and the gray floor displays the map the robot uses for navigation. (TODO: display costmaps, TF axes)

This interface, while well suited for roboticists who need to examine the low-level sensor data and messages being processed by the robot, is not very user-friendly. It also illustrates some of the difficulties inherent in robot programming, which I will detail next.

@@

\section{The way forward}
